### 2013-01-26 mcmc.tex
typography
more outline

\documentclass[12pt,twoside,pdftex]{article}

\usepackage{styles/dar_endnotes}

@@

\footnotetext{%
    The notes begin on page~\pageref{note:first}, including the
    license\note{\label{note:first}
        Copyright 2010 by the authors. This work is licensed under a
        \href{http://creativecommons.org/licenses/by-nc-nd/3.0/deed.en\_US}{%
            Creative Commons Attribution-NonCommercial-NoDerivs 3.0 Unported
            License}.}
    and the acknowledgements\note{%
        We would like to thank
          Jo Bovy (IAS),
          Brendon Brewer (Auckland),
          Jonathan Goodman (NYU),
          Dustin Lang (CMU),
          \ldots
        for valuable advice and comments.}.
}

@@

\section{What is MCMC?}

\section{Metropolis--Hastings, stretch move, and more}

...M-H, emcee, and references to competitor methods like nested and hamiltionian etc.

@@

...using the output to make figures, get numbers with error bars, and show results

@@

...tuning and Gibbs sampling and the like

...how do you know you have run long enough?

@@

@@

...Don'ts and no-nos and breaking Markov-ness.

>>>>

\documentclass[12pt,twoside,pdftex]{article}
\usepackage{styles/dar_endnotes}

@@

\footnotetext{%
    The notes begin on page~\pageref{note:first}, including the
    license\note{\label{note:first}
        Copyright 2010 by the authors. This work is licensed under a
        \href{http://creativecommons.org/licenses/by-nc-nd/3.0/deed.en\_US}{%
            Creative Commons Attribution-NonCommercial-NoDerivs 3.0 Unported
            License}.}
    and the acknowledgements\note{%
        We would like to thank
          Jo Bovy (IAS),
          Brendon Brewer (Auckland),
          Jonathan Goodman (NYU),
          Fengji Hou (NYU),
          Dustin Lang (CMU),
          \ldots
        for valuable advice and comments.}.
}

@@

\section{What is M--H MCMC?}

...The algorithm

...Why does it work (briefly)?

...What is a typical proposal distribution?

\section{stretch move and other variants}

...How does the stretch move work?

...Why is the stretch move useful?

...What, briefly, is nested sampling, and why is it good?

...What, briefly, is hamiltonian, and why is it good?

@@

...So you have a chain output, what do you do with it?

...What is the number and error bar?  What is an upper limit?

...What figures should you make to check the chain?

...How do you know you have run long enough?  Heuristically...

...Autocorrelation time

@@

...How do you make it run fast?

...Acceptance ratio and ESJD and etc.

...Gibbs sampling and interior marginalizations

@@

...Precede with optimization

...Start from different locations

...Dealing with multi-modal problems

@@

...Write and debug your own M--H sampler and then download a real
package \emph{afterwards}.

...breaking Markov-ness.

...Initialization and burn-in advice we haven't addressed earlier?

...The Bayes integral / evidence integral?

...Posterior predictive checks?
